---
title: "Household Survey Analysis"
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: true
    toc_depth: 2
    code_folding: hide
    theme: flatly
knit: (function(input, ...) { 
    rmarkdown::render( 
      input, 
      output_file = 'index.html' 
    ) 
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(lubridate)
library(knitr)
library(scales)
library(httr)
library(jsonlite)
library(kableExtra)
library(sf)
library(ggspatial)
library(gridExtra)
library(grid)
library(gtable)


# Replace with your actual token and form ID
kobo_token <- Sys.getenv("KOBO_TOKEN")
form_id <- "a7WdSwwL7Zug9hC98x5PRd"

# Define API URL (for KoboToolbox server)
base_url <- "https://kf.kobotoolbox.org/api/v2/assets/"

# Get data
response <- GET(
  paste0(base_url, form_id, "/data.json"),
  add_headers(Authorization = paste("Token", kobo_token))
)

# Parse JSON
data_list <- content(response, as = "parsed", simplifyDataFrame = TRUE)

# Convert to dataframe
kobo_data <- as.data.frame(data_list$results)

# Clean column names
names(kobo_data) <- names(kobo_data) %>%
  sub(".*/", "", .) %>%   # remove everything before the last "/"
  sub("^_", "", .)        # remove leading underscore if present

# Remove duplicate columns (keep first occurrence)
kobo_data <- kobo_data[, !duplicated(names(kobo_data))]

# Convert datetime and create date variables
kobo_data <- kobo_data %>%
  mutate(start_time = ymd_hms(start_time, tz = "UTC")) %>%
  mutate(end_time = ymd_hms(end_time, tz = "UTC")) %>%
  mutate(survey_date = as.Date(start_time)) %>%
  mutate(date_label = format(survey_date, "%b %d"))

# Convert numeric variables
numeric_vars <- c("adult_men", "adult_women", "boys", "girls", "school_age_boys", 
  "school_age_girls", "boys_attend_school", "girls_attend_school",
  "drinking_water_daily_spend", "domestic_water_daily_spend",
  "drinking_walk_time", "drinking_wait_time", "drinking_trips",
  "domestic_walk_time", "domestic_wait_time", "domestic_trips",
  "sources_access", "sources_used", "daily_helpers", "jerrycans_men",
  "jerrycans_women", "jerrycans_boys", "jerrycans_girls", "jerrycans_hired",
  "boys_late_school", "girls_late_school", "stored_amount", "sick_water",
  "injuries_water")

kobo_data <- kobo_data %>%
  mutate(across(all_of(numeric_vars), as.numeric))

# Factor community
kobo_data$community <- factor(kobo_data$community,
                              levels = c("cockle", "dworzark", "portee"),
                              labels = c("Cockle Bay", "Dworzark", "Portee Rokupa"))

# Factor surveyor_name
kobo_data$surveyor_name <- factor(kobo_data$surveyor_name,
                                  levels = c("abdulaib", "abdulaik", "boboieh", "jamiatu", "musa", "joana", "moses", "joseph", "other"),
                                  labels = c("Abdulai B", "Abdulai K", "Boboieh", "Jamiatu", "Musa", "Joana", "Moses", "Joseph", "Other"))

# Factor survey_month
kobo_data$survey_month <- factor(kobo_data$survey_month,
                                 levels = c("november", "december", "january", "february", "march", "april", "may", "june", "july", "august", "september", "october"),
                                 labels = c("November", "December", "January", "February", "March", "April", "May", "June", "July", "August", "September", "October"))

# Factor frequency variables
frequency_vars <- c("hwise_worry", "hwise_interrupted", "hwise_clothes", "hwise_schedule", 
                    "hwise_food", "hwise_hand_washing", "hwise_body_washing", "hwise_drinking", 
                    "hwise_angry", "hwise_thirsty", "hwise_no_water", "hwise_stigma", 
                    "sachet_frequency", "women_danger_environment", "men_danger_environment", 
                    "women_bullying_owner", "women_bullying_others", "women_danger_people", 
                    "men_danger_people", "treatment_frequency")

for(var in frequency_vars) {
  kobo_data[[var]] <- factor(kobo_data[[var]],
                             levels = c("never", "rarely", "sometimes", "often", "always", "dont_know", "not_applicable"),
                             labels = c("Never (0 times)", "Rarely (1-2 times)", "Sometimes (3-10 times)", 
                                       "Often (11-20 times)", "Always (More than 20 times)", "Don't know", "Not Applicable"))
}

# Create hwise score variables
hwise_vars <- c("hwise_worry", "hwise_interrupted", "hwise_clothes", "hwise_schedule", 
                "hwise_food", "hwise_hand_washing", "hwise_body_washing", "hwise_drinking", 
                "hwise_angry", "hwise_thirsty", "hwise_no_water", "hwise_stigma")

for(var in hwise_vars) {
  score_var <- paste0(var, "_score")
  kobo_data[[score_var]] <- as.integer(kobo_data[[var]])
  kobo_data[[score_var]] <- ifelse(kobo_data[[score_var]] == 1, 0,  # Never = 0
                            ifelse(kobo_data[[score_var]] == 2, 1,  # Rarely = 1
                            ifelse(kobo_data[[score_var]] == 3, 2,  # Sometimes = 2
                            ifelse(kobo_data[[score_var]] %in% c(4, 5), 3,  # Often/Always = 3
                                   NA))))  # Don't know and Not Applicable = NA
}

# Calculate total HWISE score
score_vars <- paste0(hwise_vars, "_score")
kobo_data$hwise_total_score <- rowSums(kobo_data[, score_vars], na.rm = TRUE)

# Place hwise score columns after hwise_stigma
kobo_data <- kobo_data %>%
  relocate(all_of(score_vars), hwise_total_score, .after = hwise_stigma)

# Factor yes/no variables
yes_no_vars <- c("own_water_source", "source_meets_needs", "training_received", 
                 "drinking_potable", "domestic_potable", "standing_water")

kobo_data <- kobo_data %>%
  mutate(across(all_of(yes_no_vars), 
                ~factor(., levels = c("yes", "no"), labels = c("Yes", "No"))))

# Factor gender variables
kobo_data$respondent_gender <- factor(kobo_data$respondent_gender,
                                      levels = c("male", "female"),
                                      labels = c("Male", "Female"))

kobo_data$hh_gender <- factor(kobo_data$hh_gender,
                              levels = c("male", "female"),
                              labels = c("Male", "Female"))

# Factor share_source
kobo_data$share_source <- factor(kobo_data$share_source,
                                 levels = c("household_friends", "close_friends", "anybody"),
                                 labels = c("Household and close friends", "Close friends", "Anybody"))

# Factor source type variables
kobo_data$drinking_source_type <- factor(kobo_data$drinking_source_type,
                                         levels = c("openwell", "closedwell", "privatetap", "publictap",
                                                   "surfacewater", "spring", "tank", "sachet", "personal_source"),
                                         labels = c("Open Well", "Closed Well", "Private Tap", "Public Tap",
                                                   "Surface Water", "Spring", "Tank", "Sachet", "My own source"))

kobo_data$domestic_source_type <- factor(kobo_data$domestic_source_type,
                                         levels = c("openwell", "closedwell", "privatetap", "publictap",
                                                   "surfacewater", "spring", "tank", "sachet", "personal_source"),
                                         labels = c("Open Well", "Closed Well", "Private Tap", "Public Tap",
                                                   "Surface Water", "Spring", "Tank", "Sachet", "My own source"))

# Factor collection_time
kobo_data$collection_time <- factor(kobo_data$collection_time,
                                    levels = c("morning", "afternoon", "evening", "night", "varies"),
                                    labels = c("Morning", "Afternoon", "Evening", "Night (9pm-3am)", "Varies"))

# Factor morning_specific_time
kobo_data$morning_specific_time <- factor(kobo_data$morning_specific_time,
                                         levels = c("1am", "2am", "3am", "4am", "5am", "6am", "7am", "8am", 
                                                   "9am", "10am", "11am", "12pm"),
                                         labels = c("1am", "2am", "3am", "4am", "5am", "6am", "7am", "8am", 
                                                   "9am", "10am", "11am", "12pm"))

# Factor collection_freq
kobo_data$collection_freq <- factor(kobo_data$collection_freq,
                                    levels = c("three_per_day", "two_per_day", "every_2_days", "weekly", "biweekly", "tobiweekly"),
                                    labels = c("3 times per day", "2 times per day", "Every 2 days", "Weekly", "Biweekly", "Up to biweekly"))

# Factor treatment type
kobo_data$treatment_type <- factor(kobo_data$treatment_type,
                                   levels = c("simplefilter", "boil", "chlorine", "bottle"),
                                   labels = c("Simple Filter", "Boil", "Chlorine", "Bottle"))

# Remove unnecessary columns
kobo_data <- kobo_data %>%
  select(-c(id, start_time, end_time, consent, hhid, "_version__":submitted_by))
```

# Survey Progress
## Surveys Per Day by Surveyor
```{r}
# Create daily survey counts by surveyor
daily_surveys <- kobo_data %>%
  group_by(date_label, surveyor_name) %>%
  summarise(n_surveys = n(), .groups = 'drop') %>%
  pivot_wider(names_from = surveyor_name, values_from = n_surveys, values_fill = 0) %>%
  mutate(Total = rowSums(select(., -date_label), na.rm = TRUE))

# Create and add total row
bind_rows(
  daily_surveys,
  daily_surveys %>%
    summarise(across(where(is.numeric), sum)) %>%
    mutate(date_label = "TOTAL", .before = 1)
) %>%
  kable(align = c("l", rep("c", ncol(daily_surveys))),
        col.names = c("Date", names(daily_surveys)[-1])) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

## Surveys Per Day by Community
```{r}
# Create daily survey counts by community
daily_surveys_community <- kobo_data %>%
  group_by(date_label, community) %>%
  summarise(n_surveys = n(), .groups = 'drop') %>%
  pivot_wider(names_from = community, values_from = n_surveys, values_fill = 0) %>%
  mutate(Total = rowSums(select(., -date_label), na.rm = TRUE))

# Create and add total row
bind_rows(
  daily_surveys_community,
  daily_surveys_community %>%
    summarise(across(where(is.numeric), sum)) %>%
    mutate(date_label = "TOTAL", .before = 1)
) %>%
  kable(align = c("l", rep("c", ncol(daily_surveys_community))),
        col.names = c("Date", names(daily_surveys_community)[-1])) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

# Mapping

```{r}
# Read the shapefiles
cockle_shapefile <- st_read("shapefiles/CockleBay.shp")
portee_shapefile <- st_read("shapefiles/PorteeRokupa.shp")
dworzark_shapefile <- st_read("shapefiles/Dworzark.shp")
# Filter data for each community and convert to sf object
cockle_sources <- kobo_data %>%
  filter(community == "Cockle Bay", !is.na(gps_location)) %>%
  separate(gps_location, into = c("latitude", "longitude", "altitude", "accuracy"), 
           sep = " ", remove = FALSE, convert = TRUE) %>%
  filter(!is.na(latitude), !is.na(longitude)) %>%
  mutate(day_name = factor(weekdays(survey_date), 
                     levels = c("Thursday", "Friday", "Saturday", "Sunday", "Monday", "Tuesday", "Wednesday"))
  ) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326)

portee_sources <- kobo_data %>%
  filter(community == "Portee Rokupa", !is.na(gps_location)) %>%
  separate(gps_location, into = c("latitude", "longitude", "altitude", "accuracy"), 
           sep = " ", remove = FALSE, convert = TRUE) %>%
  filter(!is.na(latitude), !is.na(longitude)) %>%
  mutate(day_name = factor(weekdays(survey_date), 
                     levels = c("Thursday", "Friday", "Saturday", "Sunday", "Monday", "Tuesday", "Wednesday"))
  ) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326)

dworzark_sources <- kobo_data %>%
  filter(community == "Dworzark", !is.na(gps_location)) %>%
  separate(gps_location, into = c("latitude", "longitude", "altitude", "accuracy"), 
           sep = " ", remove = FALSE, convert = TRUE) %>%
  filter(!is.na(latitude), !is.na(longitude)) %>%
  mutate(day_name = factor(weekdays(survey_date), 
                     levels = c("Thursday", "Friday", "Saturday", "Sunday", "Monday", "Tuesday", "Wednesday"))
  ) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326)

# Define day colors (starting with Thursday)
day_colors <- c(
  "Thursday" = "#9370DB",   # Purple
  "Friday" = "#4169E1",     # Blue
  "Saturday" = "#32CD32",   # Green
  "Sunday" = "#FFD700",     # Yellow
  "Monday" = "#FF8C00",     # Orange
  "Tuesday" = "#FF0000",    # Red
  "Wednesday" = "#808080"   # Gray
)

# Function to create labels with counts for all days
create_day_labels <- function(sources_data) {
  day_levels <- c("Thursday", "Friday", "Saturday", "Sunday", "Monday", "Tuesday", "Wednesday")
  counts <- sources_data %>%
    st_drop_geometry() %>%
    count(day_name, .drop = FALSE)
  all_days <- data.frame(day_name = factor(day_levels, levels = day_levels))
  counts_full <- left_join(all_days, counts, by = "day_name") %>%
    mutate(n = replace_na(n, 0),
           label = paste0(as.character(day_name), " (n=", n, ")"))
  setNames(counts_full$label, as.character(counts_full$day_name))
}

# Create labels for each community
cockle_labels <- create_day_labels(cockle_sources)
portee_labels <- create_day_labels(portee_sources)
dworzark_labels <- create_day_labels(dworzark_sources)

# Cockle Bay map
ggplot() +
  annotation_map_tile(type = "osm", zoomin = 0) +
  geom_sf(data = cockle_shapefile, fill = NA, color = "black", linewidth = 1) +
  geom_sf(data = cockle_sources, aes(fill = day_name), 
          size = 3, shape = 21, color = "black", stroke = 1) +
  scale_fill_manual(values = day_colors, labels = cockle_labels, 
                    breaks = c("Thursday", "Friday", "Saturday", "Sunday", "Monday", "Tuesday", "Wednesday"),
                    drop = FALSE) +
  labs(title = "Water Sources in Cockle Bay", fill = "Day Mapped") +
  theme_minimal() +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank())

# Portee Rokupa map
ggplot() +
  annotation_map_tile(type = "osm", zoomin = 0) +
  geom_sf(data = portee_shapefile, fill = NA, color = "black", linewidth = 1) +
  geom_sf(data = portee_sources, aes(fill = day_name), 
          size = 3, shape = 21, color = "black", stroke = 1) +
  scale_fill_manual(values = day_colors, labels = portee_labels,
                    breaks = c("Thursday", "Friday", "Saturday", "Sunday", "Monday", "Tuesday", "Wednesday"),
                    drop = FALSE) +
  labs(title = "Water Sources in Portee Rokupa", fill = "Day Mapped") +
  theme_minimal() +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank())

# Dworzark map
ggplot() +
  annotation_map_tile(type = "osm", zoomin = 0) +
  geom_sf(data = dworzark_shapefile, fill = NA, color = "black", linewidth = 1) +
  geom_sf(data = dworzark_sources, aes(fill = day_name), 
          size = 3, shape = 21, color = "black", stroke = 1) +
  scale_fill_manual(values = day_colors, labels = dworzark_labels,
                    breaks = c("Thursday", "Friday", "Saturday", "Sunday", "Monday", "Tuesday", "Wednesday"),
                    drop = FALSE) +
  labs(title = "Water Sources in Dworzark", fill = "Day Mapped") +
  theme_minimal() +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank())
```

# Demographics
## Household Head Gender
```{r}
# Count of household head gender by community
hh_gender_by_community <- kobo_data %>%
  group_by(community, hh_gender) %>%
  summarise(count = n(), .groups = "drop") %>%
  pivot_wider(names_from = community, values_from = count, values_fill = 0) %>%
  mutate(Total = rowSums(select(., -hh_gender), na.rm = TRUE))

# Calculate percentages for each community (columns sum to 100%)
hh_gender_percentages <- hh_gender_by_community %>%
  mutate(across(-hh_gender, ~{
    col_total <- sum(.)
    paste0(., " (", round(. / col_total * 100, 1), "%)")
  }))

# Add total row
total_row <- hh_gender_by_community %>%
  summarise(across(where(is.numeric), sum, na.rm = TRUE)) %>%
  mutate(hh_gender = "TOTAL", .before = 1) %>%
  mutate(across(where(is.numeric), ~paste0(., " (100.0%)")))

# Combine and display
hh_gender_with_total <- bind_rows(hh_gender_percentages, total_row)

hh_gender_with_total %>%
  kable(align = c("l", rep("c", ncol(.) - 1))) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```


## Household Composition by Community
```{r}
# Function to create household composition table for a community
create_hh_composition_table <- function(data, community_name) {
  # Filter for the community
  community_data <- data %>%
    filter(community == community_name)
  
  # Calculate community average household size
  community_avg_hh <- community_data %>%
    mutate(total_hh = adult_men + adult_women + boys + girls) %>%
    summarise(avg = mean(total_hh, na.rm = TRUE)) %>%
    pull(avg) %>%
    round(1)
  
  # Calculate averages and percentages for males
  male_stats <- community_data %>%
    summarise(
      adult_men_avg = mean(adult_men, na.rm = TRUE),
      boys_avg = mean(boys, na.rm = TRUE),
      total_male = adult_men_avg + boys_avg
    ) %>%
    mutate(
      adult_men_pct = adult_men_avg / community_avg_hh * 100,
      boys_pct = boys_avg / community_avg_hh * 100,
      total_male_pct = total_male / community_avg_hh * 100
    )
  
  # Calculate averages and percentages for females
  female_stats <- community_data %>%
    summarise(
      adult_women_avg = mean(adult_women, na.rm = TRUE),
      girls_avg = mean(girls, na.rm = TRUE),
      total_female = adult_women_avg + girls_avg
    ) %>%
    mutate(
      adult_women_pct = adult_women_avg / community_avg_hh * 100,
      girls_pct = girls_avg / community_avg_hh * 100,
      total_female_pct = total_female / community_avg_hh * 100
    )
  
  # Create table
  composition_table <- data.frame(
    Category = c("Adult Men", "Boys", "TOTAL MALE", "", "Adult Women", "Girls", "TOTAL FEMALE"),
    Avg = c(round(male_stats$adult_men_avg, 1), 
            round(male_stats$boys_avg, 1),
            round(male_stats$total_male, 1),
            "",
            round(female_stats$adult_women_avg, 1),
            round(female_stats$girls_avg, 1),
            round(female_stats$total_female, 1)),
    Pct = c(paste0(round(male_stats$adult_men_pct, 1), "%"),
            paste0(round(male_stats$boys_pct, 1), "%"),
            paste0(round(male_stats$total_male_pct, 1), "%"),
            "",
            paste0(round(female_stats$adult_women_pct, 1), "%"),
            paste0(round(female_stats$girls_pct, 1), "%"),
            paste0(round(female_stats$total_female_pct, 1), "%"))
  )
  
  # Create title
  title <- textGrob(paste0(community_name, "\n(Avg HH Size: ", community_avg_hh, ")"), 
                    gp = gpar(fontsize = 11, fontface = "bold"),
                  vjust = 3)
  
  # Create table grob
  table <- tableGrob(composition_table, rows = NULL, 
                     theme = ttheme_default(base_size = 9))
  
  # Combine title and table
  arrangeGrob(title, table, ncol = 1, heights = c(0.02, 0.92))
}

# Create tables for each community
cockle_table <- create_hh_composition_table(kobo_data, "Cockle Bay")
portee_table <- create_hh_composition_table(kobo_data, "Portee Rokupa")
dworzark_table <- create_hh_composition_table(kobo_data, "Dworzark")

# Arrange side by side
grid.arrange(cockle_table, portee_table, dworzark_table, ncol = 3)
```


## Water Spending
```{r fig.width=10, fig.height=4}
# Create histogram for drinking water daily spend
drinking_plot <- kobo_data %>%
  filter(!is.na(drinking_water_daily_spend)) %>%
  ggplot(aes(x = drinking_water_daily_spend)) +
  geom_histogram(bins = 20, fill = "steelblue", color = "black") +
  labs(title = paste0("Drinking Water Daily Spend (n=", sum(!is.na(kobo_data$drinking_water_daily_spend)), ")"),
       x = "Daily Spend (Leones)",
       y = "Frequency") +
  theme_minimal()

# Create histogram for domestic water daily spend
domestic_plot <- kobo_data %>%
  filter(!is.na(domestic_water_daily_spend)) %>%
  ggplot(aes(x = domestic_water_daily_spend)) +
  geom_histogram(bins = 20, fill = "steelblue", color = "black") +
  labs(title = paste0("Domestic Water Daily Spend (n=", sum(!is.na(kobo_data$domestic_water_daily_spend)), ")"),
       x = "Daily Spend (Leones)",
       y = "Frequency") +
  theme_minimal()

# Arrange plots
grid.arrange(drinking_plot, domestic_plot, ncol = 2)
```

## Water Source Ownership and Training
```{r fig.width=9, fig.height=2.5}
# Function to create yes/no table for a community
create_yes_no_table <- function(data, community_name) {
  # Filter for the community
  community_data <- data %>%
    filter(community == community_name)
  
  # Create yes/no questions data frame
  yes_no_data <- data.frame(
    Question = character(),
    Yes = character(),
    No = character(),
    stringsAsFactors = FALSE
  )
  
  # Own water source
  own_counts <- community_data %>%
    count(own_water_source) %>%
    mutate(pct = n / sum(n) * 100)
  yes_no_data <- rbind(yes_no_data, data.frame(
    Question = "Own Water Source",
    Yes = paste0(own_counts$n[own_counts$own_water_source == "Yes"], " (", round(own_counts$pct[own_counts$own_water_source == "Yes"], 1), "%)"),
    No = paste0(own_counts$n[own_counts$own_water_source == "No"], " (", round(own_counts$pct[own_counts$own_water_source == "No"], 1), "%)")
  ))
  
  # Source meets needs
  meets_needs_counts <- community_data %>%
    count(source_meets_needs) %>%
    mutate(pct = n / sum(n) * 100)
  yes_no_data <- rbind(yes_no_data, data.frame(
    Question = "Source Meets Needs",
    Yes = paste0(meets_needs_counts$n[meets_needs_counts$source_meets_needs == "Yes"], " (", round(meets_needs_counts$pct[meets_needs_counts$source_meets_needs == "Yes"], 1), "%)"),
    No = paste0(meets_needs_counts$n[meets_needs_counts$source_meets_needs == "No"], " (", round(meets_needs_counts$pct[meets_needs_counts$source_meets_needs == "No"], 1), "%)")
  ))
  
  # Training received
  training_counts <- community_data %>%
    count(training_received) %>%
    mutate(pct = n / sum(n) * 100)
  yes_no_data <- rbind(yes_no_data, data.frame(
    Question = "Training Received",
    Yes = paste0(training_counts$n[training_counts$training_received == "Yes"], " (", round(training_counts$pct[training_counts$training_received == "Yes"], 1), "%)"),
    No = paste0(training_counts$n[training_counts$training_received == "No"], " (", round(training_counts$pct[training_counts$training_received == "No"], 1), "%)")
  ))
  
  # Drinking potable
  drinking_potable_counts <- community_data %>%
    count(drinking_potable) %>%
    mutate(pct = n / sum(n) * 100)
  yes_no_data <- rbind(yes_no_data, data.frame(
    Question = "Drinking Water Potable",
    Yes = paste0(drinking_potable_counts$n[drinking_potable_counts$drinking_potable == "Yes"], " (", round(drinking_potable_counts$pct[drinking_potable_counts$drinking_potable == "Yes"], 1), "%)"),
    No = paste0(drinking_potable_counts$n[drinking_potable_counts$drinking_potable == "No"], " (", round(drinking_potable_counts$pct[drinking_potable_counts$drinking_potable == "No"], 1), "%)")
  ))
  
  # Domestic potable
  domestic_potable_counts <- community_data %>%
    count(domestic_potable) %>%
    mutate(pct = n / sum(n) * 100)
  yes_no_data <- rbind(yes_no_data, data.frame(
    Question = "Domestic Water Potable",
    Yes = paste0(domestic_potable_counts$n[domestic_potable_counts$domestic_potable == "Yes"], " (", round(domestic_potable_counts$pct[domestic_potable_counts$domestic_potable == "Yes"], 1), "%)"),
    No = paste0(domestic_potable_counts$n[domestic_potable_counts$domestic_potable == "No"], " (", round(domestic_potable_counts$pct[domestic_potable_counts$domestic_potable == "No"], 1), "%)")
  ))
  
  # Standing water
  standing_water_counts <- community_data %>%
    count(standing_water) %>%
    mutate(pct = n / sum(n) * 100)
  yes_no_data <- rbind(yes_no_data, data.frame(
    Question = "Standing Water",
    Yes = paste0(standing_water_counts$n[standing_water_counts$standing_water == "Yes"], " (", round(standing_water_counts$pct[standing_water_counts$standing_water == "Yes"], 1), "%)"),
    No = paste0(standing_water_counts$n[standing_water_counts$standing_water == "No"], " (", round(standing_water_counts$pct[standing_water_counts$standing_water == "No"], 1), "%)")
  ))
  
  # Create title
  title <- textGrob(community_name, 
                    gp = gpar(fontsize = 11, fontface = "bold"),
                    vjust = 1)
  
  # Create table grob
  table <- tableGrob(yes_no_data, rows = NULL, 
                     theme = ttheme_default(base_size = 9,
                                           padding = unit(c(2, 2), "mm")))
  
  # Combine title and table
  arrangeGrob(title, table, ncol = 1, heights = c(0.08, 0.92))
}

# Create tables for each community
cockle_table <- create_yes_no_table(kobo_data, "Cockle Bay")
portee_table <- create_yes_no_table(kobo_data, "Portee Rokupa")
dworzark_table <- create_yes_no_table(kobo_data, "Dworzark")

# Arrange side by side
grid.arrange(cockle_table, portee_table, dworzark_table, ncol = 3)
```

# HWISE
```{r}
# Get survey counts by community
survey_counts <- kobo_data %>%
  count(community) %>%
  mutate(label = paste0(community, " (n=", n, ")"))

# Calculate mean for each HWISE score variable by community
hwise_summary <- kobo_data %>%
  group_by(community) %>%
  summarise(
    across(all_of(c(score_vars, "hwise_total_score")),
           ~mean(., na.rm = TRUE),
           .names = "{.col}")
  ) %>%
  pivot_longer(cols = -community,
               names_to = "Variable",
               values_to = "Mean") %>%
  mutate(
    Variable = case_when(
      Variable == "hwise_worry_score" ~ "Worry",
      Variable == "hwise_interrupted_score" ~ "Interrupted",
      Variable == "hwise_clothes_score" ~ "Clothes",
      Variable == "hwise_schedule_score" ~ "Schedule",
      Variable == "hwise_food_score" ~ "Food",
      Variable == "hwise_hand_washing_score" ~ "Hand Washing",
      Variable == "hwise_body_washing_score" ~ "Body Washing",
      Variable == "hwise_drinking_score" ~ "Drinking",
      Variable == "hwise_angry_score" ~ "Angry",
      Variable == "hwise_thirsty_score" ~ "Thirsty",
      Variable == "hwise_no_water_score" ~ "No Water",
      Variable == "hwise_stigma_score" ~ "Stigma",
      Variable == "hwise_total_score" ~ "Total Score",
      TRUE ~ Variable
    ),
    Mean = round(Mean, 2)
  ) %>%
  pivot_wider(names_from = community, values_from = Mean)

# Create column names with counts
col_names <- c("Variable", survey_counts$label)

# Display table
hwise_summary %>%
  kable(align = c("l", "c", "c", "c"),
        col.names = col_names) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

# Water Sources
## Sources Access Distribution
```{r fig.width=10, fig.height=4}
# Create histogram for sources_access by community
cockle_access <- kobo_data %>%
  filter(community == "Cockle Bay", !is.na(sources_access)) %>%
  ggplot(aes(x = sources_access)) +
  geom_histogram(bins = 15, fill = "steelblue", color = "black") +
  labs(title = paste0("Cockle Bay (n=", sum(!is.na(kobo_data$sources_access[kobo_data$community == "Cockle Bay"])), ")"),
       x = "Count",
       y = "Frequency") +
  theme_minimal()

portee_access <- kobo_data %>%
  filter(community == "Portee Rokupa", !is.na(sources_access)) %>%
  ggplot(aes(x = sources_access)) +
  geom_histogram(bins = 15, fill = "steelblue", color = "black") +
  labs(title = paste0("Portee Rokupa (n=", sum(!is.na(kobo_data$sources_access[kobo_data$community == "Portee Rokupa"])), ")"),
       x = "Count",
       y = "Frequency") +
  theme_minimal()

dworzark_access <- kobo_data %>%
  filter(community == "Dworzark", !is.na(sources_access)) %>%
  ggplot(aes(x = sources_access)) +
  geom_histogram(bins = 15, fill = "steelblue", color = "black") +
  labs(title = paste0("Dworzark (n=", sum(!is.na(kobo_data$sources_access[kobo_data$community == "Dworzark"])), ")"),
       x = "Count",
       y = "Frequency") +
  theme_minimal()

# Arrange plots with overall title
grid.arrange(
  top = textGrob("Sources Access", gp = gpar(fontsize = 14, fontface = "bold")),
  cockle_access, portee_access, dworzark_access, 
  ncol = 3
)
```

## Sources Used Distribution
```{r fig.width=10, fig.height=4}
# Create histogram for sources_used by community
cockle_used <- kobo_data %>%
  filter(community == "Cockle Bay", !is.na(sources_used)) %>%
  ggplot(aes(x = sources_used)) +
  geom_histogram(bins = 15, fill = "steelblue", color = "black") +
  labs(title = paste0("Cockle Bay (n=", sum(!is.na(kobo_data$sources_used[kobo_data$community == "Cockle Bay"])), ")"),
       x = "Count",
       y = "Frequency") +
  theme_minimal()

portee_used <- kobo_data %>%
  filter(community == "Portee Rokupa", !is.na(sources_used)) %>%
  ggplot(aes(x = sources_used)) +
  geom_histogram(bins = 15, fill = "steelblue", color = "black") +
  labs(title = paste0("Portee Rokupa (n=", sum(!is.na(kobo_data$sources_used[kobo_data$community == "Portee Rokupa"])), ")"),
       x = "Count",
       y = "Frequency") +
  theme_minimal()

dworzark_used <- kobo_data %>%
  filter(community == "Dworzark", !is.na(sources_used)) %>%
  ggplot(aes(x = sources_used)) +
  geom_histogram(bins = 15, fill = "steelblue", color = "black") +
  labs(title = paste0("Dworzark (n=", sum(!is.na(kobo_data$sources_used[kobo_data$community == "Dworzark"])), ")"),
       x = "Count",
       y = "Frequency") +
  theme_minimal()

# Arrange plots with overall title
grid.arrange(
  top = textGrob("Sources Used", gp = gpar(fontsize = 14, fontface = "bold")),
  cockle_used, portee_used, dworzark_used, 
  ncol = 3
)
```

## Sachet Frequency by Community
```{r}
# Count of sachet frequency by community
sachet_by_community <- kobo_data %>%
  group_by(community, sachet_frequency) %>%
  summarise(count = n(), .groups = "drop") %>%
  pivot_wider(names_from = community, values_from = count, values_fill = 0) %>%
  mutate(Total = rowSums(select(., -sachet_frequency), na.rm = TRUE))

# Calculate percentages for each community (columns sum to 100%)
sachet_percentages <- sachet_by_community %>%
  mutate(across(-sachet_frequency, ~{
    col_total <- sum(.)
    paste0(., " (", round(. / col_total * 100, 1), "%)")
  }))

# Add total row
total_row <- sachet_by_community %>%
  summarise(across(where(is.numeric), sum, na.rm = TRUE)) %>%
  mutate(sachet_frequency = "TOTAL", .before = 1) %>%
  mutate(across(where(is.numeric), ~paste0(., " (100.0%)")))

# Combine and display
sachet_with_total <- bind_rows(sachet_percentages, total_row)

sachet_with_total %>%
  kable(align = c("l", rep("c", ncol(.) - 1))) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

## Water Collection Time by Community
```{r}
# Combine collection_time and morning_specific_time
kobo_data_combined <- kobo_data %>%
  mutate(
    combined_time = case_when(
      collection_time == "Morning" & !is.na(morning_specific_time) ~ as.character(morning_specific_time),
      !is.na(collection_time) ~ as.character(collection_time),
      TRUE ~ NA_character_
    ),
    # Set order for combined_time
    combined_time = factor(combined_time, 
                          levels = c("1am", "2am", "3am", "4am", "5am", "6am", "7am", "8am", 
                                    "9am", "10am", "11am", "12pm", "Afternoon", "Evening", 
                                    "Night (9pm-3am)", "Varies"))
  )

# Count of combined time by community
time_by_community <- kobo_data_combined %>%
  group_by(community, combined_time, .drop = FALSE) %>%
  summarise(count = n(), .groups = "drop") %>%
  pivot_wider(names_from = community, values_from = count, values_fill = 0) %>%
  mutate(Total = rowSums(select(., -combined_time), na.rm = TRUE))

# Calculate percentages for each community (columns sum to 100%)
time_percentages <- time_by_community %>%
  mutate(across(-combined_time, ~{
    col_total <- sum(.)
    paste0(., " (", round(. / col_total * 100, 1), "%)")
  }))

# Add total row
total_row <- time_by_community %>%
  summarise(across(where(is.numeric), sum, na.rm = TRUE)) %>%
  mutate(combined_time = "TOTAL", .before = 1) %>%
  mutate(across(where(is.numeric), ~paste0(., " (100.0%)")))

# Combine and display
time_with_total <- bind_rows(time_percentages, total_row)

time_with_total %>%
  kable(align = c("l", rep("c", ncol(.) - 1)),
        col.names = c("Collection Time", names(time_by_community)[-1])) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

## Collection Frequency by Community
```{r}
# Count of collection frequency by community
freq_by_community <- kobo_data %>%
  group_by(community, collection_freq) %>%
  summarise(count = n(), .groups = "drop") %>%
  pivot_wider(names_from = community, values_from = count, values_fill = 0) %>%
  mutate(Total = rowSums(select(., -collection_freq), na.rm = TRUE))

# Calculate percentages for each community (columns sum to 100%)
freq_percentages <- freq_by_community %>%
  mutate(across(-collection_freq, ~{
    col_total <- sum(.)
    paste0(., " (", round(. / col_total * 100, 1), "%)")
  }))

# Add total row
total_row <- freq_by_community %>%
  summarise(across(where(is.numeric), sum, na.rm = TRUE)) %>%
  mutate(collection_freq = "TOTAL", .before = 1) %>%
  mutate(across(where(is.numeric), ~paste0(., " (100.0%)")))

# Combine and display
freq_with_total <- bind_rows(freq_percentages, total_row)

freq_with_total %>%
  kable(align = c("l", rep("c", ncol(.) - 1))) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

# Water Gathering
## Daily Helpers Distribution by Community
```{r fig.width=12, fig.height=4}
# Create histogram for daily_helpers by community
cockle_helpers <- kobo_data %>%
  filter(community == "Cockle Bay", !is.na(daily_helpers)) %>%
  ggplot(aes(x = daily_helpers)) +
  geom_histogram(bins = 15, fill = "steelblue", color = "black") +
  labs(title = paste0("Cockle Bay (n=", sum(!is.na(kobo_data$daily_helpers[kobo_data$community == "Cockle Bay"])), ")"),
       x = "Count",
       y = "Frequency") +
  theme_minimal()

portee_helpers <- kobo_data %>%
  filter(community == "Portee Rokupa", !is.na(daily_helpers)) %>%
  ggplot(aes(x = daily_helpers)) +
  geom_histogram(bins = 15, fill = "steelblue", color = "black") +
  labs(title = paste0("Portee Rokupa (n=", sum(!is.na(kobo_data$daily_helpers[kobo_data$community == "Portee Rokupa"])), ")"),
       x = "Count",
       y = "Frequency") +
  theme_minimal()

dworzark_helpers <- kobo_data %>%
  filter(community == "Dworzark", !is.na(daily_helpers)) %>%
  ggplot(aes(x = daily_helpers)) +
  geom_histogram(bins = 15, fill = "steelblue", color = "black") +
  labs(title = paste0("Dworzark (n=", sum(!is.na(kobo_data$daily_helpers[kobo_data$community == "Dworzark"])), ")"),
       x = "Count",
       y = "Frequency") +
  theme_minimal()

# Arrange plots with overall title
grid.arrange(
  top = textGrob("Daily Helpers", gp = gpar(fontsize = 14, fontface = "bold")),
  cockle_helpers, portee_helpers, dworzark_helpers, 
  ncol = 3
)
```

## Jerrycans Carried by Gender
```{r fig.height=1.5, fig.width=8}
# Function to create jerrycan table for a community
create_jerrycan_table <- function(data, community_name) {
  # Filter for the community
  community_data <- data %>%
    filter(community == community_name)
  
  # Calculate totals for each category
  men_total <- sum(community_data$jerrycans_men, na.rm = TRUE)
  boys_total <- sum(community_data$jerrycans_boys, na.rm = TRUE)
  women_total <- sum(community_data$jerrycans_women, na.rm = TRUE)
  girls_total <- sum(community_data$jerrycans_girls, na.rm = TRUE)
  hired_total <- sum(community_data$jerrycans_hired, na.rm = TRUE)
  
  # Calculate grand total
  grand_total <- men_total + boys_total + women_total + girls_total + hired_total
  
  # Create table
  jerrycan_table <- data.frame(
    Category = c("Children", "Adults", "Hired"),
    Male = c(paste0(boys_total, " (", round(boys_total / grand_total * 100, 1), "%)"),
             paste0(men_total, " (", round(men_total / grand_total * 100, 1), "%)"),
             paste0(hired_total, " (", round(hired_total / grand_total * 100, 1), "%)")),
    Female = c(paste0(girls_total, " (", round(girls_total / grand_total * 100, 1), "%)"),
               paste0(women_total, " (", round(women_total / grand_total * 100, 1), "%)"),
               "")
  )
  
  # Create title
  title <- textGrob(community_name, 
                    gp = gpar(fontsize = 11, fontface = "bold"),
                    vjust = 1)
  
  # Create table grob
  table <- tableGrob(jerrycan_table, rows = NULL, 
                     theme = ttheme_default(base_size = 9,
                                           padding = unit(c(2, 2), "mm")))
  
  # Combine title and table
  arrangeGrob(title, table, ncol = 1, heights = c(0.08, 0.92))
}

# Create tables for each community
cockle_table <- create_jerrycan_table(kobo_data, "Cockle Bay")
portee_table <- create_jerrycan_table(kobo_data, "Portee Rokupa")
dworzark_table <- create_jerrycan_table(kobo_data, "Dworzark")

# Arrange side by side
grid.arrange(cockle_table, portee_table, dworzark_table, ncol = 3)
```

## School Days Missed by Community
```{r}
# Filter for households with school-age children
school_data <- kobo_data %>%
  filter(school_age_boys > 0 | school_age_girls > 0)

# Calculate statistics by community
late_school_summary <- school_data %>%
  group_by(community) %>%
  summarise(
    # Any child missed
    hh_missed = sum(boys_late_school > 0 | girls_late_school > 0, na.rm = TRUE),
    total_hh = n(),
    pct_missed = hh_missed / total_hh * 100,
    avg_days = mean((boys_late_school + girls_late_school)[(boys_late_school > 0 | girls_late_school > 0)], na.rm = TRUE)
  ) %>%
  mutate(
    count_pct = paste0(hh_missed, " (", round(pct_missed, 1), "%)"),
    avg_days = as.character(round(avg_days, 1))
  ) %>%
  select(community, count_pct, avg_days) %>%
  pivot_longer(cols = -community,
               names_to = "Metric",
               values_to = "Value") %>%
  mutate(
    Metric = case_when(
      Metric == "count_pct" ~ "Households with Children Missing School",
      Metric == "avg_days" ~ "Average Days Missed",
      TRUE ~ Metric
    )
  ) %>%
  pivot_wider(names_from = community, values_from = Value)

# Display table
late_school_summary %>%
  kable(align = c("l", "c", "c", "c")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE)
```

# Water and Health
## Stored Water Amount Distribution by Community
```{r fig.width=12, fig.height=4}
# Create histogram for stored_amount by community
cockle_stored <- kobo_data %>%
  filter(community == "Cockle Bay", !is.na(stored_amount)) %>%
  ggplot(aes(x = stored_amount)) +
  geom_histogram(bins = 15, fill = "steelblue", color = "black") +
  labs(title = paste0("Cockle Bay (n=", sum(!is.na(kobo_data$stored_amount[kobo_data$community == "Cockle Bay"])), ")"),
       x = "Count",
       y = "Frequency") +
  theme_minimal()

portee_stored <- kobo_data %>%
  filter(community == "Portee Rokupa", !is.na(stored_amount)) %>%
  ggplot(aes(x = stored_amount)) +
  geom_histogram(bins = 15, fill = "steelblue", color = "black") +
  labs(title = paste0("Portee Rokupa (n=", sum(!is.na(kobo_data$stored_amount[kobo_data$community == "Portee Rokupa"])), ")"),
       x = "Count",
       y = "Frequency") +
  theme_minimal()

dworzark_stored <- kobo_data %>%
  filter(community == "Dworzark", !is.na(stored_amount)) %>%
  ggplot(aes(x = stored_amount)) +
  geom_histogram(bins = 15, fill = "steelblue", color = "black") +
  labs(title = paste0("Dworzark (n=", sum(!is.na(kobo_data$stored_amount[kobo_data$community == "Dworzark"])), ")"),
       x = "Count",
       y = "Frequency") +
  theme_minimal()

# Arrange plots with overall title
grid.arrange(
  top = textGrob("Stored Water Amount", gp = gpar(fontsize = 14, fontface = "bold")),
  cockle_stored, portee_stored, dworzark_stored, 
  ncol = 3
)
```

## Sick from Water Distribution by Community
```{r fig.width=12, fig.height=4}
# Create histogram for sick_water by community
cockle_sick <- kobo_data %>%
  filter(community == "Cockle Bay", !is.na(sick_water)) %>%
  ggplot(aes(x = sick_water)) +
  geom_histogram(bins = 15, fill = "steelblue", color = "black") +
  labs(title = paste0("Cockle Bay (n=", sum(!is.na(kobo_data$sick_water[kobo_data$community == "Cockle Bay"])), ")"),
       x = "Count",
       y = "Frequency") +
  theme_minimal()

portee_sick <- kobo_data %>%
  filter(community == "Portee Rokupa", !is.na(sick_water)) %>%
  ggplot(aes(x = sick_water)) +
  geom_histogram(bins = 15, fill = "steelblue", color = "black") +
  labs(title = paste0("Portee Rokupa (n=", sum(!is.na(kobo_data$sick_water[kobo_data$community == "Portee Rokupa"])), ")"),
       x = "Count",
       y = "Frequency") +
  theme_minimal()

dworzark_sick <- kobo_data %>%
  filter(community == "Dworzark", !is.na(sick_water)) %>%
  ggplot(aes(x = sick_water)) +
  geom_histogram(bins = 15, fill = "steelblue", color = "black") +
  labs(title = paste0("Dworzark (n=", sum(!is.na(kobo_data$sick_water[kobo_data$community == "Dworzark"])), ")"),
       x = "Count",
       y = "Frequency") +
  theme_minimal()

# Arrange plots with overall title
grid.arrange(
  top = textGrob("Sick from Water", gp = gpar(fontsize = 14, fontface = "bold")),
  cockle_sick, portee_sick, dworzark_sick, 
  ncol = 3
)
```

## Injuries from Water Distribution by Community
```{r fig.width=12, fig.height=4}
# Create histogram for injuries_water by community
cockle_injuries <- kobo_data %>%
  filter(community == "Cockle Bay", !is.na(injuries_water)) %>%
  ggplot(aes(x = injuries_water)) +
  geom_histogram(bins = 15, fill = "steelblue", color = "black") +
  labs(title = paste0("Cockle Bay (n=", sum(!is.na(kobo_data$injuries_water[kobo_data$community == "Cockle Bay"])), ")"),
       x = "Count",
       y = "Frequency") +
  theme_minimal()

portee_injuries <- kobo_data %>%
  filter(community == "Portee Rokupa", !is.na(injuries_water)) %>%
  ggplot(aes(x = injuries_water)) +
  geom_histogram(bins = 15, fill = "steelblue", color = "black") +
  labs(title = paste0("Portee Rokupa (n=", sum(!is.na(kobo_data$injuries_water[kobo_data$community == "Portee Rokupa"])), ")"),
       x = "Count",
       y = "Frequency") +
  theme_minimal()

dworzark_injuries <- kobo_data %>%
  filter(community == "Dworzark", !is.na(injuries_water)) %>%
  ggplot(aes(x = injuries_water)) +
  geom_histogram(bins = 15, fill = "steelblue", color = "black") +
  labs(title = paste0("Dworzark (n=", sum(!is.na(kobo_data$injuries_water[kobo_data$community == "Dworzark"])), ")"),
       x = "Count",
       y = "Frequency") +
  theme_minimal()

# Arrange plots with overall title
grid.arrange(
  top = textGrob("Injuries from Water", gp = gpar(fontsize = 14, fontface = "bold")),
  cockle_injuries, portee_injuries, dworzark_injuries, 
  ncol = 3
)
```

## Treatment Type by Community
```{r}
# Process the select_multiple data for treatment_type
# Split the treatment_type values and count occurrences
treatment_counts <- kobo_data %>%
  mutate(treatment_type_list = strsplit(as.character(treatment_type), " ")) %>%
  unnest(treatment_type_list) %>%
  mutate(
    treatment_type_list = case_when(
      treatment_type_list == "simplefilter" ~ "Simple Filter",
      treatment_type_list == "boil" ~ "Boil",
      treatment_type_list == "chlorine" ~ "Chlorine",
      treatment_type_list == "bottle" ~ "Bottle",
      TRUE ~ treatment_type_list
    )
  ) %>%
  group_by(community, treatment_type_list) %>%
  summarise(count = n(), .groups = "drop")

# Get total households per community
total_hh <- kobo_data %>%
  count(community, name = "total")

# Join and calculate percentages
treatment_summary <- treatment_counts %>%
  left_join(total_hh, by = "community") %>%
  mutate(
    pct = count / total * 100,
    count_pct = paste0(count, " (", round(pct, 1), "%)")
  ) %>%
  select(community, treatment_type_list, count_pct) %>%
  pivot_wider(names_from = community, values_from = count_pct, values_fill = "0 (0.0%)")

# Display table
treatment_summary %>%
  kable(col.names = c("Treatment Type", "Cockle Bay", "Dworzark", "Portee Rokupa"),
        align = c("l", "c", "c", "c")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE)
```

## Water-Related Disease by Community
```{r}
# Process the select_multiple data for water_disease
# Split the water_disease values and count occurrences
disease_counts <- kobo_data %>%
  mutate(water_disease_list = strsplit(as.character(water_disease), " ")) %>%
  unnest(water_disease_list) %>%
  mutate(
    water_disease_list = case_when(
      water_disease_list == "cholera" ~ "Cholera",
      water_disease_list == "typhoid" ~ "Typhoid",
      water_disease_list == "malaria" ~ "Malaria",
      water_disease_list == "diarrhea" ~ "Diarrhea",
      water_disease_list == "dysentery" ~ "Dysentery",
      water_disease_list == "skinrashes" ~ "Skin Rashes",
      water_disease_list == "eyeinfection" ~ "Eye Infection",
      TRUE ~ water_disease_list
    )
  ) %>%
  group_by(community, water_disease_list) %>%
  summarise(count = n(), .groups = "drop")

# Get total households per community
total_hh <- kobo_data %>%
  count(community, name = "total")

# Join and calculate percentages
disease_summary <- disease_counts %>%
  left_join(total_hh, by = "community") %>%
  mutate(
    pct = count / total * 100,
    count_pct = paste0(count, " (", round(pct, 1), "%)")
  ) %>%
  select(community, water_disease_list, count_pct) %>%
  pivot_wider(names_from = community, values_from = count_pct, values_fill = "0 (0.0%)")

# Display table
disease_summary %>%
  kable(col.names = c("Disease", "Cockle Bay", "Dworzark", "Portee Rokupa"),
        align = c("l", "c", "c", "c")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE)
```